---
title: "Prepregancy Obesity and ADHD"
author: "Victor Wang"
date: "June 19, 2015"
output: html_document
---

```{r, echo=FALSE, results='asis', include=FALSE}
library(ipw)
library(dplyr)
library(xtable)
setwd('~/niches/')
# alles <- read.sas7bdat('nest_merge_tb_rc.sas7bdat')
# save(alles, file = "nest_merge_tb_rc.Rdata")
load(file='nest_merge_tb_rc.Rdata')
dat_wg <- filter(alles, age_mo_SR_Surv <= 72 & GestAge_TotalDays >= 238)
dat_wg <- subset(dat_wg, select=c(BASC_APHY, BASC_AP, BASC_HY, 
                                  BRF_IN, BRF_SF, BRF_EC, BRF_WM, BRF_PO, BRF_GEC, # BRF_ISCI, BRF_FI, BRF_EMI, 
                                  BMI_LMP_kgm2, gest_weight_gain_kg, mat_gest_wt_gain_category, 
                                  parity_3cat, BABY_WEIGHT, age_mo_SR_Surv, mom_age_delv, race_final, 
                                  BABY_GENDER, education_final, GestAge_TotalDays, maternal_smoking2, ASRS_THRSH))

dat_wg <- dat_wg[dat_wg$race_final!="",]
dat_wg$education_final <- sub("/", "_", dat_wg$education_final)
dat_wg$educ.f <- factor(dat_wg$education_final, exclude = "")
contrasts(dat_wg$educ.f) <- contr.treatment(4, base=4)
dat_wg$race.f <- factor(dat_wg$race_final)
contrasts(dat_wg$race.f) <- contr.treatment(4, base=4)
dat_wg$parity.f <- factor(dat_wg$parity_3cat)
dat_wg$smoker.f <- factor(dat_wg$maternal_smoking2)
dat_wg$gender.f <- factor(dat_wg$BABY_GENDER)
dat_wg$asrs_thrsh.f <- factor(dat_wg$ASRS_THRSH)
dat_wg$mat_gest_wt_gain_category[dat_wg$mat_gest_wt_gain_category == "missing BMI LMP or Gest wt gain"] <- NA
dat_wg$mat_gest_wt_gain_c3.f <- factor(dat_wg$mat_gest_wt_gain_category)
contrasts(dat_wg$mat_gest_wt_gain_c3.f) <- contr.treatment(3, base=1)

dat_wg <- na.omit(dat_wg)
dat_bmi <- dat_wg
dat_wg <- filter(dat_wg, age_mo_SR_Surv <= 66 & GestAge_TotalDays >= 238)

```

## This one examines gestational weight gain as the predictor of ADHD symptoms – would need to model the “treatment” as a categorical variable with 3 levels. 

```{r, echo=FALSE, include=FALSE, fig.show='asis'}
ipw_wt <- function() {
  temp <- ipwpoint(exposure = mat_gest_wt_gain_c3.f, family = "multinomial", link = "logit",
                   numerator = ~ 1, denominator = ~ BMI_LMP_kgm2 + parity.f + BABY_WEIGHT + age_mo_SR_Surv +
                     mom_age_delv + race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
                   data = na.omit(dat_wg))
  dat_wg$sw <- temp$ipw.weights
  msm <- (svyglm(outcome ~ mat_gest_wt_gain_c3.f, design = svydesign(~ 1, weights = ~ sw, data = dat_wg)))
  results <- summary(msm)$coef[2:3, c(1, 4)]
  results <- round(results, digits=3)
  results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
}
lm_wt <- function() {
  lm_wg <- lm(outcome ~ mat_gest_wt_gain_c3.f + BMI_LMP_kgm2 + parity.f + BABY_WEIGHT + age_mo_SR_Surv +
                mom_age_delv + race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
              data = na.omit(dat_wg))
  results <- summary(lm_wg)$coef[2:3, c(1, 4)]
  results <- round(results, digits=3)
  results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
}
outcome_vars <- select(dat_wg, BASC_APHY, BASC_AP, BASC_HY, BRF_IN, BRF_SF, BRF_EC, BRF_WM, BRF_PO, BRF_GEC)
outcome_vnames <- names(outcome_vars)
ipw_wt_all <- NULL
lm_wt_all <- NULL
for (outcome_n in 1:length(outcome_vars)) {
  dat_wg$outcome <- outcome_vars[, outcome_n]
  ipw_wt_all <- cbind(ipw_wt_all, ipw_wt())
  lm_wt_all <- cbind(lm_wt_all, lm_wt())
}
```
```{r, echo=FALSE, fig.show='asis', results='asis'}
ipw_wt_all.table <- xtable(ipw_wt_all, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(ipw_wt_all.table, type='html')
```

### Traditional regression models

```{r, echo=FALSE, fig.show='asis', results='asis'}
lm_wt_all.table <- xtable(lm_wt_all, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(lm_wt_all.table, type='html')
```

## This one examines prepregnancy BMI on a continuous score as a predictor of ADHD symptoms – would need to model the “treatment” as continuous in the IPW method 

```{r, echo=TRUE, include=FALSE, fig.show='asis'}
ipw_bmi <- function() {
  temp <- ipwpoint(exposure = BMI_LMP_kgm2, family = "gaussian", 
                   numerator = ~ 1, denominator = ~ gest_weight_gain_kg + parity.f + BABY_WEIGHT + 
                     age_mo_SR_Surv + mom_age_delv + 
                     race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
                   data = na.omit(dat_bmi))
  dat_bmi$sw <- temp$ipw.weights
  msm <- (svyglm(outcome ~ BMI_LMP_kgm2, design = svydesign(~ 1, weights = ~ sw, data = dat_bmi)))
  results <- summary(msm)$coef[2, c(1, 4)]
  results <- round(results, digits=3)
  results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
}
lm_bmi <- function() {
  lm_bmi <- lm(outcome ~ BMI_LMP_kgm2 + gest_weight_gain_kg + parity.f + BABY_WEIGHT + age_mo_SR_Surv + 
                 mom_age_delv + race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
               data = na.omit(dat_bmi))
  results <- summary(lm_bmi)$coef[2, c(1, 4)]
  results <- round(results, digits=3)
  results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
}
outcome_vars <- select(dat_bmi, BASC_APHY, BASC_AP, BASC_HY, BRF_IN, BRF_SF, BRF_EC, BRF_WM, BRF_PO, BRF_GEC)
outcome_vnames <- names(outcome_vars)

ipw_bmi_all <- NULL
lm_bmi_all <- NULL
for (outcome_n in 1:length(outcome_vars)) {
  dat_bmi$outcome <- outcome_vars[, outcome_n]
  ipw_bmi_all <- cbind(ipw_bmi_all, ipw_bmi())
  lm_bmi_all <- cbind(lm_bmi_all, lm_bmi())
}
rownames(ipw_bmi_all)[2] <- "BMI"
rownames(lm_bmi_all)[2] <- "BMI"
```

```{r, echo=FALSE, fig.show='asis', results='asis'}
ipw_bmi_all.table <- xtable(ipw_bmi_all, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(ipw_bmi_all.table, type='html')
```

### Traditional regression models

```{r, echo=FALSE, fig.show='asis', results='asis'}
lm_bmi_all.table <- xtable(lm_bmi_all, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(lm_bmi_all.table, type='html')
```
