---
title: "Prepregancy Obesity and ADHD"
author: "Victor Wang"
date: "June 19, 2015"
output: html_document
---

```{r, echo=FALSE, results='asis', include=FALSE}
library(ipw)
library(dplyr)
library(xtable)
setwd('~/niches/')
# alles <- read.sas7bdat('nest_merge_tb_rc.sas7bdat')
# save(alles, file = "nest_merge_tb_rc.Rdata")
load(file='nest_merge_tb_rc.Rdata')
dat_wg <- filter(alles, age_mo_SR_Surv <= 72 & GestAge_TotalDays >= 238)
dat_wg <- subset(dat_wg, select=c(BASC_APHY, BASC_AP, BASC_HY, 
                                  BRF_IN, BRF_SF, BRF_EC, BRF_WM, BRF_PO, BRF_GEC, # BRF_ISCI, BRF_FI, BRF_EMI, 
                                  BMI_LMP_kgm2, gest_weight_gain_kg, mat_gest_wt_gain_category, 
                                  parity_3cat, BABY_WEIGHT, age_mo_SR_Surv, mom_age_delv, race_final, 
                                  BABY_GENDER, education_final, GestAge_TotalDays, maternal_smoking2, ASRS_THRSH))

dat_wg <- dat_wg[dat_wg$race_final!="",]
dat_wg$education_final <- sub("/", "_", dat_wg$education_final)
dat_wg$educ.f <- factor(dat_wg$education_final, exclude = "")
contrasts(dat_wg$educ.f) <- contr.treatment(4, base=4)
dat_wg$race.f <- factor(dat_wg$race_final)
contrasts(dat_wg$race.f) <- contr.treatment(4, base=4)
dat_wg$parity.f <- factor(dat_wg$parity_3cat)
dat_wg$smoker.f <- factor(dat_wg$maternal_smoking2)
dat_wg$gender.f <- factor(dat_wg$BABY_GENDER)
dat_wg$asrs_thrsh.f <- factor(dat_wg$ASRS_THRSH)
dat_wg$mat_gest_wt_gain_category[dat_wg$mat_gest_wt_gain_category == "missing BMI LMP or Gest wt gain"] <- NA
dat_wg$mat_gest_wt_gain_c3.f <- factor(dat_wg$mat_gest_wt_gain_category)
contrasts(dat_wg$mat_gest_wt_gain_c3.f) <- contr.treatment(3, base=1)

dat_wg$bmic5.f <- factor(cut(dat_wg$BMI_LMP_kgm2, c(0, 18.5, 25, 30, 35, 40, 100), right=F))
dat_wg$baby_weight.f <- factor(cut(dat_wg$BABY_WEIGHT, c(0, 2500, 4200, Inf), right=F))
dat_wg$gestage.f <- factor(cut((dat_wg$GestAge_TotalDays / 7), c(0, 37, 41, Inf), right=F))
dat_wg$mom_age_delv.f <- factor(cut(dat_wg$mom_age_delv, c(0, 25, 30, 35, Inf), right=F))
# contrasts(nwaz$bmic5.f) <- contr.treatment(6, base=2)

dat_wg <- na.omit(dat_wg)
dat_bmi <- dat_wg
dat_wg <- filter(dat_wg, age_mo_SR_Surv <= 66 & GestAge_TotalDays >= 238)

```

```{r, results="asis", echo=F}
fvar <- subset(dat_wg, select=c(mom_age_delv.f, educ.f, race.f, parity.f, asrs_thrsh.f, smoker.f, bmic5.f, mat_gest_wt_gain_c3.f, gestage.f, baby_weight.f, BABY_GENDER))
cvar <- subset(dat_wg, select=c(BASC_APHY, BRF_GEC))

# tblFun <- function(x){
#     tbl <- table(x)
#     # cbind(tbl, round(prop.table(tbl)*100, 0))
#     df <- data.frame(cbind(tbl, round(prop.table(tbl)*100, 0)))
#     names(df) <- c("n", "pct")
#     df
# }
# p.table <- sapply(fvar, tblFun)
# lapply(p.table, cbind)
# p.table <- data.frame(rbind(p.table))

tblFun <- function(x){
    tbl <- table(x)
    prop <- round(prop.table(tbl)*100,0)
    prop
    # cbind(tbl, round(prop.table(tbl)*100, 0))
}
des.table <- cbind(
  data.frame(unlist(apply(fvar, 2, table))),
  data.frame(unlist(apply(fvar, 2, tblFun))),
  round(data.frame(unlist(apply(fvar, 2, function(x) by(cvar$BASC_APHY, x, mean)))), 2),
  round(data.frame(unlist(apply(fvar, 2, function(x) by(cvar$BASC_APHY, x, sd)))), 1),
  round(data.frame(unlist(apply(fvar, 2, function(x) by(cvar$BRF_GEC, x, mean)))), 2),
  round(data.frame(unlist(apply(fvar, 2, function(x) by(cvar$BRF_GEC, x, sd)))), 1)
)
for (i in 1:ncol(des.table)) {
  des.table[,i] <- as.character(des.table[,i])
}
names(des.table) <- c('n', '(%)', "Mean", "(SD)", "Mean", "(SD)")
des.table[, 2] <- paste0("(", des.table[, 2], ")")
des.table[, 4] <- paste0("(", des.table[, 4], ")")
des.table[, 6] <- paste0("(", des.table[, 6], ")")

write.csv(des.table, file="des.table.csv")

des.table <- xtable(des.table, include.rownames=FALSE) # html.table.attributes=list(font.size=7pt)
# digits(des.table)[c(2,6)] <- 0
print(des.table, type='html')

```


## This one examines gestational weight gain as the predictor of ADHD symptoms – would need to model the “treatment” as a categorical variable with 3 levels. 

```{r, echo=FALSE, include=FALSE, fig.show='asis'}
ipw_wt <- function() {
  temp <- ipwpoint(exposure = mat_gest_wt_gain_c3.f, family = "multinomial", link = "logit",
                   numerator = ~ 1, denominator = ~ BMI_LMP_kgm2 + parity.f + BABY_WEIGHT + age_mo_SR_Surv +
                     mom_age_delv + race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
                   data = na.omit(dat_wg))
  dat_wg$sw <- temp$ipw.weights
  msm <- (svyglm(outcome ~ mat_gest_wt_gain_c3.f, design = svydesign(~ 1, weights = ~ sw, data = dat_wg)))
  # results <- matrix(summary(msm)$coef[2:3, c(1, 2, 4)], 2, 3)
  results <- data.frame(summary(msm)$coef[2:3, c(1, 2, 4)])
  results$cat <- rownames(results)
  results$out <- outcome_vnames[outcome_n]
  # rownames(results) <- outcome_vnames[outcome_n]
  # results[, c(1, 2)] <- round(results[, c(1, 2)], digits=2)
  # results[, 3] <- round(results[, 3], digits=3)
  # results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
  return(results)
}
lm_wt <- function() {
  lm_wg <- lm(outcome ~ mat_gest_wt_gain_c3.f + BMI_LMP_kgm2 + parity.f + BABY_WEIGHT + age_mo_SR_Surv +
                mom_age_delv + race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
              data = na.omit(dat_wg))
  results <- data.frame(summary(lm_wg)$coef[2:3, c(1, 2, 4)])
  results$cat <- rownames(results)
  results$out <- outcome_vnames[outcome_n]
  # results <- round(results, digits=3)
  # results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
  return(results)
}
outcome_vars <- select(dat_wg, BASC_APHY, BASC_HY, BASC_AP, BRF_GEC, BRF_IN, BRF_SF, BRF_EC, BRF_WM, BRF_PO)
outcome_vnames <- names(outcome_vars)
ipw_wt_all <- NULL
lm_wt_all <- NULL
for (outcome_n in 1:length(outcome_vars)) {
  dat_wg$outcome <- outcome_vars[, outcome_n]
  ipw_wt_all <- rbind(ipw_wt_all, ipw_wt())
  lm_wt_all <- rbind(lm_wt_all, lm_wt())
}
# ipw_wt_all$cat <- strtrim(rownames(ipw_wt_all), 22)
ipw_wt_all$cat <- substr(ipw_wt_all$cat, 22, 22)
ipw_wt_all_w <- reshape(ipw_wt_all, timevar = "cat", idvar=c("out"), direction = "wide")

lm_wt_all$cat <- substr(lm_wt_all$cat, 22, 22)
lm_wt_all_w <- reshape(lm_wt_all, timevar = "cat", idvar=c("out"), direction = "wide")
```
```{r, echo=FALSE, fig.show='asis', results='asis'}
ipw_wt_all.table <- xtable(ipw_wt_all_w, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(ipw_wt_all.table, type='html')
```

### Traditional regression models

```{r, echo=FALSE, fig.show='asis', results='asis'}
lm_wt_all.table <- xtable(lm_wt_all_w, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(lm_wt_all.table, type='html')
```

## This one examines prepregnancy BMI on a continuous score as a predictor of ADHD symptoms – would need to model the “treatment” as continuous in the IPW method 

```{r, echo=TRUE, include=FALSE, fig.show='asis'}
ipw_bmi <- function() {
  temp <- ipwpoint(exposure = BMI_LMP_kgm2, family = "gaussian", 
                   numerator = ~ 1, denominator = ~ gest_weight_gain_kg + parity.f + BABY_WEIGHT + 
                     age_mo_SR_Surv + mom_age_delv + 
                     race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
                   data = na.omit(dat_bmi))
  dat_bmi$sw <- temp$ipw.weights
  msm <- (svyglm(outcome ~ BMI_LMP_kgm2, design = svydesign(~ 1, weights = ~ sw, data = dat_bmi)))
  results <- summary(msm)$coef[2, c(1, 2, 4)]
  # results <- summary(msm)$coef[2, c(1, 2, 4)]
  # rownames(results) <- outcome_vnames[outcome_n]
  # results[, c(1, 2)] <- round(results[, c(1, 2)], digits=2)
  # results[, 3] <- round(results[, 3], digits=3)
  return(results)
  # results <- cbind(outcome_vnames[outcome_n], results)
  # results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
}
lm_bmi <- function() {
  lm_bmi <- lm(outcome ~ BMI_LMP_kgm2 + gest_weight_gain_kg + parity.f + BABY_WEIGHT + age_mo_SR_Surv + 
                 mom_age_delv + race.f + gender.f + educ.f + GestAge_TotalDays + smoker.f + asrs_thrsh.f, 
               data = na.omit(dat_bmi))
  results <- summary(lm_bmi)$coef[2, c(1, 2, 4)]
  results <- round(results, digits=3)
  # results <- rbind(c(dim(dat_wg)[1], outcome_vnames[outcome_n]), results)
}
outcome_vars <- select(dat_bmi, BASC_APHY, BASC_HY, BASC_AP, BRF_GEC, BRF_IN, BRF_SF, BRF_EC, BRF_WM, BRF_PO)
outcome_vnames <- names(outcome_vars)

ipw_bmi_all <- NULL
lm_bmi_all <- NULL
for (outcome_n in 1:length(outcome_vars)) {
  dat_bmi$outcome <- outcome_vars[, outcome_n]
  ipw_bmi_all <- rbind(ipw_bmi_all, ipw_bmi())
  lm_bmi_all <- rbind(lm_bmi_all, lm_bmi())
}
# rownames(ipw_bmi_all)[2] <- "BMI"
# rownames(lm_bmi_all)[2] <- "BMI"
```

```{r, echo=FALSE, fig.show='asis', results='asis'}
ipw_bmi_all.table <- xtable(ipw_bmi_all, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(ipw_bmi_all.table, type='html')
```

### Traditional regression models

```{r, echo=FALSE, fig.show='asis', results='asis'}
lm_bmi_all.table <- xtable(lm_bmi_all, include.rownames=FALSE)
# digits(des.table)[c(2,6)] <- 0
print(lm_bmi_all.table, type='html')
```
